An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-18 EconGrowthSeminar.Rnw
Now have a macro for placing scaled graphics at a specific location on the page. Using that macro for placing a US flag on pages that include US data in the presentation.

@@

@@

\begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_us.pdf} Single-Factor Fit} %----------------------------
<<Results_Table_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
sfUSK <- singleFactorModel("US", "K")
sfUSL <- singleFactorModel("US", "L")
sfUSQ <- singleFactorModel("US", "Q")
sfUSX <- singleFactorModel("US", "X")
sfUSU <- singleFactorModel("US", "U")
@
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \sfEqn
        \vspace{\baselineskip}

        \tiny
          \begin{tabular}{|c|c|c|}\hline
            $f$   & $\lambda$                      & $m$\\
            \hline
            $k$   & \Sexpr{coef(sfUSK)["lambda"]}  & \Sexpr{coef(sfUSK)["m"]}\\
            \hline
            $l$   & \Sexpr{coef(sfUSL)["lambda"]}  & \Sexpr{coef(sfUSL)["m"]}\\
            \hline
            $q$   & \Sexpr{coef(sfUSQ)["lambda"]}  & \Sexpr{coef(sfUSQ)["m"]}\\
            \hline
            $x$   & \Sexpr{coef(sfUSX)["lambda"]}  & \Sexpr{coef(sfUSX)["m"]}\\
            \hline
            $u$   & \Sexpr{coef(sfUSU)["lambda"]}  & \Sexpr{coef(sfUSU)["m"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
\end{frame}

>>>>

\usepackage{tikz} % To use the tikzpicture environment.

@@

% Places an image (with scaling) at a position on the page
% Arguments:
%  #1 image path
%  #2 image scaling (1.0 = same size as original image, 2.0 = double size)
%  #3 x offset from center of the frame (include units, if desired. e.g. "1.0in")
%  #4 y offset from center of the frame (include units, if desired. e.g. "1.0in")
\newcommand{\putat}[4]{
  \begin{tikzpicture}[remember picture,overlay] 
    \node [xshift=#3, yshift=#4] at (current page.center){
      \includegraphics[scale=#2]{#1}
    };             
  \end{tikzpicture}
}

@@

\begin{frame}{Single-Factor $y$ Predictions} %----------------------------

<<Results_Table_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
sfUSK <- singleFactorModel("US", "K")
sfUSL <- singleFactorModel("US", "L")
sfUSQ <- singleFactorModel("US", "Q")
sfUSX <- singleFactorModel("US", "X")
sfUSU <- singleFactorModel("US", "U")
@
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \sfEqn
        \vspace{\baselineskip}

        \tiny
          \begin{tabular}{|c|c|c|}\hline
            $f$   & $\lambda$                      & $m$\\
            \hline
            $k$   & \Sexpr{coef(sfUSK)["lambda"]}  & \Sexpr{coef(sfUSK)["m"]}\\
            \hline
            $l$   & \Sexpr{coef(sfUSL)["lambda"]}  & \Sexpr{coef(sfUSL)["m"]}\\
            \hline
            $q$   & \Sexpr{coef(sfUSQ)["lambda"]}  & \Sexpr{coef(sfUSQ)["m"]}\\
            \hline
            $x$   & \Sexpr{coef(sfUSX)["lambda"]}  & \Sexpr{coef(sfUSX)["m"]}\\
            \hline
            $u$   & \Sexpr{coef(sfUSU)["lambda"]}  & \Sexpr{coef(sfUSU)["m"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward on the frame.
  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
\end{frame}
